---
title: "Project 2 Doc"
output: html_document
---

Created by: David Tran, Juliette Seive, Boris Boukhonine

*"Catches of fish, crustaceans, molluscs and other aquatic organisms are reported in whole tonnes live weight (TLW) per species, fishing area, country and year."*

**Countries Key**

Code  Country
BG	 Bulgaria
ES	 Spain
DK	 Denmark
DE	 Germany
BE	 Belgium
IE	 Ireland
EE	 Estonia
FR	 France
IT	 Italy
LV	 Latvia
LT	 Lithuania
NL	 Netherlands
PL	 Poland
PT	 Portugal
RO	 Romania
FI	 Finland
SE	 Sweden
UK	 United Kingdom (E+W+S+NI)
UKM	 Scotland
IS	 Iceland
NO	 Norway
FO	 Faeroe Islands (DK)
GG	 Guernsey
IM	 Isle of Man
JE	 Jersey
RU	 Russia
SJ	 Svalbard and Jan Mayen
UA	 Ukraine
LY	 Libya
CV	 Cape Verde
GL	 Greenland (DK)
US	 United States
PA	 Panama
CN	 China (including Hong Kong)
JP	 Japan
KR	 South Korea
TW	 Taiwan
OUT	 Outbound

**Plots are as follows**\

1) Total fish weights by species per country for 2013 \ 

2) Counted fish weights for various species from 2007 to 2013 for France
Filtered out all weight below 10000 tons.\ 

3) Comparison of France and Spain over years\ 
Filtered out all weights below 10000 tons

**Load packages and fetch data**
```{r}
source("../01 Data/package_loader.R", echo = TRUE)
source("../01 Data/dataframe.R", echo=TRUE)
```

**Wrangle the data**
```{r}
source("../02 Data_Wrangling/wrangling.R", echo=TRUE)

```

